### 2020-05-12 README.Rmd
address winbuilder NOTES

## Contributor Code of Conduct
Please note that this project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

## Contributor Code of Conduct
Please note that this project is released with a [Contributor Code of Conduct](https://slu-opengis.github.io/areal/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
